---
title: |
  | \vspace{13cm} \LARGE\textcolor{white}{\textbf{PSET 3: Balance}}
subtitle: \LARGE\textcolor{white}{\textbf{EDU S598 | Dr.Susan Dynarski}}
author: \LARGE\textcolor{white}{\textbf{Dean Kaplan}}
date: \LARGE\textcolor{white}{\textbf{October 3, 2023}}
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
header-includes:
-  \AddToShipoutPictureBG{\ifthenelse{\value{page}<2}{\AtPageLowerLeft{{\includegraphics[width=17in,height=20in]{comp5.jpg}}}}{}}
output: 
  pdf_document:
    latex_engine: xelatex
    fig_caption: false
    keep_tex: true

    includes:
      in_header: header.tex

    
always_allow_html: yes
---
\thispagestyle{firstpage}  
\newpage
\tableofcontents
\newpage
\definecolor{hightlightColor}{HTML}{FFFF66}



```{r define_function, include=F, echo=FALSE,fig.width = 1, fig.height=2, fig.align='center',results = 'asis'}
#libraries we will use
library(knitr)
library(flextable)
library(dplyr)
library(magrittr)
#load data
data= haven::read_dta("mindspark_balance.dta")
options(knitr.kable.NA = '')


#declare function that accepts a list of dataframes as a tuple where index 1 = treatment rows and index 2 = control row, and two string vectors, First is our variables to describe and second are the row labels
#this function will fashion and format our tables

table_maker <- function(data_subsets,vars,row_labels){
  
  #nice to use them seperate sometimes
  treatment = data_subsets[[1]]
  control = data_subsets[[2]]
  #will use together for t-tests
  both = rbind(treatment,control)
  #these are the title rows, rest of row will be blank, will come back to this in a moment
  titles = grep("#",row_labels)
  #once we add the rows in, there will be some reshuffling so this is accounting for that reshuffle
  title_index = (titles-(1:length(titles)-1))
  
  #first column, var means for treatment
  treatment_mean_vector = treatment %>% summarise(mean=apply(.[vars],2,mean,na.rm=T))
  
   #Second column, var means for control
  control_mean_vector = control %>% summarise(mean=apply(.[vars],2,mean,na.rm=T))
  
  #third column, their difference
  difference_vector = round(treatment_mean_vector-control_mean_vector,3)
  
  #Column 4, se vector of stderror in difference between treatment and control for each var
  se_vector = unlist(lapply(vars, function(x) round(t.test(formula = formula(paste0(x, "~control")),data = both)$stderr,3)))
  
  #column 5, N rows of data for each var in treatment
  treatment_n = round(treatment %>% summarise(obs=apply(.[vars],2,function(x) sum(!is.na(x)))),2)
  
  #column 6, N rows of data for each var in control
  control_n = round(control %>% summarise(obs=apply(.[vars],2,function(x) sum(!is.na(x)))),2)
  
  #append columns to make dataframe
  table = cbind(round(treatment_mean_vector,2),round(control_mean_vector,2),difference_vector,se_vector,treatment_n,control_n)

  #thank you for user helatemail from stack overflow for the next three brilliant lines that added empty rows where i needed them
  s <- sort(c(seq_len(nrow(table)), title_index))
  final_table <- table[s,]
  final_table[duplicated(s)[c(2:length(duplicated(s)),1)],] <- NA
  
  #now add row-names
  final_table = cbind(gsub("#","",row_labels),final_table)
     
  #name the columns
  names(final_table) = c(" ","Mean (treatment)","Mean (control)","Difference","Standard Error","Observations (treatment)","Observations (control)")
  
  #little bit of formatting
  formatted_table = flextable::flextable(final_table) %>% autofit()
  
  formatted_table %<>%width(j = 1, 1.95, unit = "in")
  
  formatted_table %<>%width(j = 2:7, 1, unit = "in") %>% align(j = 2:7, align="center")
  
   formatted_table %<>% align(part="header", align="center")
  
   formatted_table %<>%width(j = c(3,5), .85, unit = "in")
  
  return(formatted_table)
}

```
\newpage 

# Question 1: Replicate Table

The following data are from Muralidharan et al. (2019). \footnote{Muralidharan, Karthik, Abhijeet Singh, and Alejandro J. Ganimian. "Disrupting education? Experimental evidence on technology-aided instruction in India." American Economic Review 109.4 (2019): 1426-1460}

```{r table1, include=T, echo=FALSE,warning=F,fig.width = 1, fig.height=2, fig.align='center',results = 'asis'}
#declare row labels
row_labels = c("#Demographic characteristics", "          Female","          Age (years)","          SES index","#Grade in School    ", "          Grade 4","          Grade 5", "          Grade 6","          Grade 7","          Grade 8", "          Grade 9","#Baseline test scores    ","          Math","          Hindi","Present at endline")

#declare variables we will use
vars = c("st_female1","st_age1","ses_index","d_sch_grade4","d_sch_grade5","d_sch_grade6","d_sch_grade7","d_sch_grade8","d_sch_grade9","m_theta_mle","h_theta_mle","in_r2")

cat("## A) Table 1: Duplicating Table A ")
cat("\n\n")

#make table 1!
table_maker(list(subset(data,data$control==0&data$round==1),subset(data,data$control==1&data$round==1)),vars,row_labels )

#knit_print(table)
```

\newpage 


```{r table2, include=TRUE, echo=FALSE, warning=F, fig.width = 1, fig.height=2, fig.align='center',results = 'asis'}
cat("## B) Table 2: Duplicating Table B ")
cat("\n\n")
#knit_print(table)

#make table 2!
table_maker(list(subset(data,data$control==0&data$round==1&data$in_r2==1),subset(data,data$control==1&data$round==1&data$in_r2==1)),vars[c(-length(vars))],row_labels[c(-length(row_labels))] )

```

\newpage 

# Question 2: Added Measures

```{r table3, include=TRUE, echo=FALSE,warning=F,wfig.width = 1, fig.height=2, fig.align='center',results = 'asis'}
#two new vars
row_labels = c("#Demographic characteristics", "          Female","          Age (years)","          SES index","#Grade in School", "          Grade 4","          Grade 5", "          Grade 6","          Grade 7","          Grade 8", "          Grade 9","#Baseline test scores","          Math","          Hindi","#Added Measures","          Private Tutoring","          Private Math Tutoring","Present at endline")

#two new vars
vars = c("st_female1","st_age1","ses_index","d_sch_grade4","d_sch_grade5","d_sch_grade6","d_sch_grade7","d_sch_grade8","d_sch_grade9","m_theta_mle","h_theta_mle","any_tuition","st_tui_math_hrs","in_r2")

cat("## A) Table 3: Duplicating Table A With Added Covariates ")
cat("\n\n")

#make table 3, two new vars!
table_maker(list(subset(data,data$control==0&data$round==1),subset(data,data$control==1&data$round==1)),vars,row_labels)

#knit_print(table)
```

\newpage 

```{r table4, include=TRUE, echo=FALSE,warning=F,fig.width = 1, fig.height=2, fig.align='center',results = 'asis'}

cat("## B)Table 4: Duplicating Table B With Added Covariates ")
cat("\n\n")

#make table 4, same vars as table 3 with smaller subsample
table_maker(list(subset(data,data$control==0&data$round==1&data$in_r2==1),subset(data,data$control==1&data$round==1&data$in_r2==1)),vars[c(-length(vars))],row_labels[c(-length(row_labels))] )

#knit_print(table)


```


